---
title: "Overview"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This document introduces you to the two main functions of the package:

- `compute_cor()`
- `plot_cor()`

## Compute correlation coefficients and Cramér's V 

To explore the basics of the package, we'll use the `mtcars` dataset and the `tea` dataset.

The mtcars dataset is built-in in R and the tea dataset comes originally from the `FactoMineR` package but it's also shipped with `corr`.

<br>
Computing a correlation coefficient or the Cramér's V is simple:

```{r}
library("corr")

results <- compute_cor(tea, method = "cramer")
```

Four methods are available:

- "pearson"
- "kendall"
- "spearman"
- "cramer"

The "pearson", "kendall" or "spearman" methods should be used for numerical variables. 
See `stats::cor()` for more details.

On the other hand, the "cramer" method is usefull to measure the association between nominal variables (see the [wikipedia article](https://en.wikipedia.org/wiki/Cram%C3%A9r%27s_V) for more).

## Visualize the results

After computing the correlation, you can use the `plot_cor()` function to visualize the results with a heatmap.

```{r, fig.width=6, fig.height=6, fig.align="center"}
results <- compute_cor(mtcars, method = "pearson")
plot_cor(results)
```

<br>
Different options are available (see `help(plot_corr)` for the whole list).

For instance, we can plot only the lower triangle of the matrix, change the palette of colors and reorder the variables by an "optimal" number of groups.

```{r, fig.width=6, fig.height=6, fig.align="center"}
plot_cor(results, type = "lower", palette = "inferno", clustering = TRUE)
```
